---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  dpi = 200
)
library(prismadiagramR)
library(dplyr)
```

# prismadiagramR

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/ltrainstg/prismadiagramR.svg?branch=master)](https://travis-ci.org/ltrainstg/prismadiagramR)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ltrainstg/prismadiagramR?branch=master&svg=true)](https://ci.appveyor.com/project/ltrainstg/prismadiagramR)
[![CRAN status](https://www.r-pkg.org/badges/version/prismadiagramR)](https://CRAN.R-project.org/package=prismadiagramR)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Codecov test coverage](https://codecov.io/gh/ltrainstg/prismadiagramR/branch/master/graph/badge.svg)](https://codecov.io/gh/ltrainstg/prismadiagramR?branch=master)
<!-- badges: end -->

The goal of prismadiagramR is to create a custom prismadiagram in R. 

## Installation

You can install the released version of prismadiagramR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("prismadiagramR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ltrainstg/prismadiagramR")
```
## Example

This example shows how to create a simple automated PRISMA from a publication tracker. 



```{r}

set.seed(25)
N <- 100
studyStatus <- data.frame(Pub.ID = seq(1:N), 
                          Source = sample(1:3, N, replace = TRUE),
                          Filter = sample(1:5, N, replace = TRUE))
studyStatus$Filter[studyStatus$Filter==5] <- NA  
getPrisma(studyStatus) %>% DiagrammeR::grViz(.)

```

## Other PRISMA resources
A few other R packages exist that also make PRISMA diagram that might be better for your needs.

  1. [prismaStatement](https://cran.r-project.org/web/packages/PRISMAstatement/vignettes/PRISMA.html) This also uses DiagrammeR, but the template is fixed. 
  2. [metagear](https://rdrr.io/cran/metagear/man/plot_PRISMA.html) This does not use DiagrammeR and is highly customizable, but is buried with many other functions and a little hard to get working. 
  
## Package Development Resources
This package was developed following these guides:

  * John Muschelli's r package development 1 [HERE](https://www.youtube.com/watch?v=79s3z0gIuFU)
  * https://sahirbhatnagar.com/rpkg/#tests
  
